Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management

### 2023-07-24 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd

---
output:
  html_document: default
---
# Reply to the Reviewer #2

Your comments are in blue, and our responses are in black.

<span style = "color: blue;">This study examines the economic value associated with three statistical methods used to generate site-specific nitrogen application rates: 1) geographically weighted regressions using the method of Rakshit et al. (2020) denoted as GWR-R, 2) geographically weighted regressions using the method of Trevisan et al. (2021) denoted as GWR-T, and 3) shape-constrained additive models (SCAM). Using straightforward Monte Carlo simulations, the two GWR methods are used to determine the economically optimal nitrogen rate (EONR) and profits from variable rate applications (VRA), while the SCAM methodology is used to determine the EONRs and profits for uniform rate applications (URA). These rates are based on estimations of site-specific corn yield functions for six cells across 1,440 subplots. The authors find the GWR-T outperforms GWR-R when the nitrogen price (relative to corn) is low, but GWR-R outperforms GWR-T when the nitrogen price is relatively high. This is because of the relative over- and underestimation of the EONRs. The study also finds that both GWR-T and GWR-R may have substantially overestimated the economic value of VRA; the net benefit of VRA over URA is much smaller, roughly $2 per acre (just over $5 per hectare, on average). For convenience, my review below is organized into a set of general comments, specific comments, and comments related to the exposition and writing, with each being arranged in order of page number. All comments are designed to strengthen the research.</span>

We would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript. The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.  In return, we have attempted to carefully address each of the comments and revise the manuscript in response.

@@

<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it's spelled out in the sentence, but you should spell it out first and then use the acronym. </span>

Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript

<span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>

We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo. We have corrected it to use subscript notation (see line 3 of section 4.4). Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to $(j, i)$ both in this section and throughout the rest of the manuscript.
